### 2018-07-06 Stickleback_Paper.tex
Introduction updated

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{comment}
\usepackage[backgroundcolor=pink,linecolor=red]{todonotes}
% \usepackage{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

@@

\newcommand{\plr}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}

@@

@@

In the mid 19th century,
Darwin theorized that the process of natural selection resulted in speciation, 
meaning all living species derived from a common ancestor. 
He also believed that this process took place on ecological timescales that would not allow for 
this process to be observed in a single lifetime. 
Today, we have found evidence of evolution
in tens of generations and are starting to grasp the complexity behind such a simple idea. 
Famously, Drs. Peter and Rosemary Grant went on to study Darwin's finches and
found that phenotypes could adapt to changes in the food source within mere generations.
%more specific?
We have have found many examples of rapid adaptation in many commonly studied models
but many questions still remain surrounding the genomics which allow for this.

\plr{I like how this starts out, but going to Darwin is maybe a bit too ``big'';
    better to say that we now have a number of examples of rapid evolution;
    cite the Grants and a few others (Gough island house mice? insecticide resistance in Drosophila?),
    then move on to the sticklebacks in more detail.}

Recently, rapid and parallel adaptation has brought about question of selection of
standing genetic variation in natural populations 
of Stickleback.
In 1964, The Great Alaskan Earthquake caused Middleton island to raise up and in turn, 
introduced a group of new freshwater ponds around the perimeter of the island. 
Quickly inhabited by the surrounding marine population of Ninespine Stickleback,
we've observed significant phenotypic changes in less than 50 years that appear to be 
parallel to freshwater stickleback that have been separated for over $13,000$ years \citep{LescakE7204}.
\plr{clarify what ``parallel'' means}
\plr{``citep'' for ``cite in parentheses''. (and, citations come before the punctuation)}
In freshwater stickleback, 
the number of lateral plates are reduced
and the opercle shapes shows the same expansion of the dorsal region and reduction of the ventral region (Cite Kristin, Cresko et. al)
\plr{End with a question that the next two paragraphs propose an answer to.}

The leading hypothesis is that rather than acting on new mutations, ecological speciation is sped up through selection on standing genetic variation found in marine populations. 
\plr{Is this ``ecological speciation''? Speciation would imply the ecotypes are developing reproductive incompatibility;
    I think that we think the pattern is stable. Maybe ``adaptation to freshwater habitats''?}
One clear example of this is the gene \textit{eda} 
which has been shown to regulate the number of lateral plates. 
While this gene arose millions of years ago, 
it is found in freshwater ponds which have formed much more recently.
Novel evidence from natural populations has provided evidence that most regions of the genome that distinguish marine-freshwater genetic differences share this pattern. \cite{Nelson2017}

% In 2009, Dolph Schluter and Gina L. Conte 
\citet{schluter2009genetics} 
\plr{"citet" for "cite, as part of the text"}
suggested the ``transporter''-hypothesis.  
\plr{in latex, use ` `words' ' to get the open- and closed-double quotes (not the double-quote character)}
This outlined the flow of freshwater alleles into marine populations through offspring of hybridization events.
It suggests freshwater haplotypes are distributed though marine individuals and are continually selected upon in introduced freshwater populations.
The continued selection on freshwater favored alleles,
and introgression between the two sub-species,
allows the marine to maintain the freshwater haplotype dispersed in low frequency among its' individuals. 
Once a new freshwater environment is introduced and inhabited by marine individuals who carry freshwater adapted alleles, selection rebuilds the freshwater haplotype. \cite{schluter2009genetics} 
The alternative to this hypothesis is that individuals from other freshwater environments migrate directly to the new environments, and their haplotype is passed down directly. 
This hypothesis has been shown to be unlikely due to 
finding a high frequency of freshwater alleles in the ocean,
and almost no freshwater individuals. 
\plr{Bring up the possibility of more than one freshwater haplotype here.}

Assuming they were correct about transportation, we might ask; 
how much migration and gene flow is to be expected for this relationship to be maintained?
\plr{motivating questions need more work}
%(Other questions)
%how does selection, at the genomic level, alter given a range of migration and recombination rates?
Here, we use forward moving simulations to model marine and freshwater populations of stickleback.
We then observe the effect (focusing on migration and recombination, for now) 
of different parameters on local adaptation of introduced freshwater environments. 
We compare to real data and make predictions about realistic parameters.

\section{Methods}

Our models are forward-moving evolutionary models which
emulate the geography, selective pressure, and genomic architecture 
of coastal marine and freshwater lake populations. 
Here we give a brief overview of the software used and the models created to observe the effects of selection. 
\plr{Should focus on the model, not the software -- describe how the simulation works}
Each set of simulations was run multiple times to ensure the data we observed was ???

%(1) Correlation of mutation frequencies at low migration rates
%(2) Distribution of Effect Size? (run another set to make sure)

\subsection{SLiM}

To model the stickleback populations, we used a flexible evolutionary framework, SLiM. (cite SLiM 2) 
The model-type we used was based off of an extended wright-fisher. 
The simulation life cycle of each generation is as follows.
\plr{This can be merged with the next section, perhaps as a section called ``Life cycle''.  
    Here and below, avoid using SLiM jargon (don't say ``callback'').}
First, 
generate offspring by:
(1) choosing parents based on cached fitness values and migration rates, 
(2) performing recombination of parental genomes, 
(3) allow for mutation, 
(4) modify each child by a defined callback. 
Next, 
offspring become individuals before fitness is evaluated for the next generation.
Finally,
the generation counter is incremented. 
The population structure in SLiM can be arranged in any number of subpopulations, 
continuous or discrete, connected by any rate of migration.

\subsection{Model}

\subsubsection*{Geography}

What we've modeled geographically is a coastal marine population 
connected by migration to multiple, smaller freshwater populations that are located along the coast.
The population structure for the marine is modeled as a one-dimensional, continuous population
ranging from 0.0 to 10.0.
There are two sets of lakes which represent freshwater populations; 
the first which evolves in parallel to the marine, 
and a set introduced later in the simulation as a subset of the marine. 
In SLiM, these freshwater sets are defined as just two continuous subpopulations. 
Using SLiM?s $modifyChild()$ callback, we?ve modeled both to act as 10 separate discrete subpopulations. 
\plr{no need to say this: we will provide the SLiM recipes as supplementary material
    so that someone interested can see exactly how it works.}
Each of the $10$ lakes, $i$, is located along the marine at $i - 0.5$, 
and connected by migration only through the marine environment. 
The marine has $2000$ individuals while 
each of the lakes fluctuate around $200$.

@@

\subsubsection*{Selective Pressure}

To emulate the freshwater and marine selective pressure, 
we set up a quantitative genetics model in which fitness is phenotypically based. 
Freshwater and Marine environments are distinguished by a single numeric value. 
This value is the optimum phenotype for each environment
and acts as a representation of lateral plate number and opercle shape in the stickleback populations.
\plr{More concisely, these could be called the ``optimal trait values''.}
The fitness of an individual is then determined by a probability density for a normal distribution 
at the quantile (?) of the difference between the optimum and the individual's phenotype
\plr{instead, we can say that we use a ``Gaussian fitness function'', 
    where the fitness of an individual with trait $x$ in a population with optimal trait value $x_0$ is:}
\begin{align}
    f(x; x_0) &= \exp\left(\frac{(x - x_0)^2 }{ 2 \sigma^2}\right),
\end{align}
with $\sigma = 15$.

%     \[
% \textnormal{Individual.Fitness = } X \sim \mathcal{N}(\textnormal{Optimum - Individual.Phenotype},\,0.0\,15.0).
%     \]

Where an individual?s phenotype is also defined by a single numeric value; 
determined as a summation of the selection coefficients of all mutations an individual possesses. 
\plr{Hm. Should we say ``phenotype'' or ``trait''? I've been saying ``trait'', which is less jargon-ey?}
% no empty lines before equations, usually - they should read like part of the text itself.
	\[
{\textnormal{Individual.Phenotype = } \sum_{m \in mutations} \textnormal{m.selectionCoeff}}
	\]

\todo{This isn't quite right because of how we calculate additive, recessive, and dominant}

We allow six mutation types which affect phenotype along with one neutral mutation type.
Among the effect mutations; 
\plr{``effect mutation'' is not a standard term; should say ``mutations that affect the phenotype'' here,
    and be careful about what we call them elsewhere.}
there are additive, dominant, and recessive mutations which effect phenotype
in either the positive or negative direction. 
The selection coefficients are pulled from a beta distribution 
with a shape parameter of $1$ and a mean of either $0.5$, or ${-0.5}$. 
\plr{Can just say this in words, no need to have an equation.
    Also, a Gamma with shape 1 and mean 0.5 is an Exponential with mean 0.5.}
	\[
\textnormal{Mutation.selectionCoeff = } X \sim \Gamma (1,\pm0.5)
	\]

@@

\subsubsection*{Genomic Architecture}

\plr{This should maybe come before the phenotype.}
In SLiM, the genome is conceptually a linear array of loci defining locations for 
mutations that arise and breakpoints for recombination. 
Genomic elements define a range depicting the types of mutations that can arise, and the ratio at which different mutation types can arise. 
Although still uncertain about how much of the genome is directly associated with the distinguished phenotypes, 
GWAS has indicated clusters of loci (linkage groups? Operon?) along the genome to be causative. 
To mimic this and compare dynamics of neutral vs. effect under selection, 
we create regions of effect. 
In these genomic elements of effect, we uniformly allow additive, recessive, and dominant, mutation that can push phenotype in either the positive or negative direction to arise. 
Every genomic position outside of these effect regions only allows for selectively neutral mutations to arise.

@@

\todo{finish this}

@@

Here, we're interested in observing how different parameter values
(mainly migrations rates and recombination rates)
impact the sharing of alleles between populations. 
\plr{Below, I think we should make sure to use ``population'' to mean either ``lake'' or ``ocean'';
    so when we compute freshwater-marine $F_{ST}$ this measures differentiation between habitats,
    not between populations.}
we define freshwater adapted alleles (FAA),
\plr{I vote to remove the abbreviations. Also, should make the dependence on generation more clear: maybe ``freshwater adapted alleles at time $t$''?}
at any given generation,
to be a mutations with a frequency higher than $0.5$ in \textit{any} of the original lakes, 
while remaining lower than $0.5$ in the marine. 
This is because the transportation hypothesis does not specify where or when an advantageous mutation arises; 
but simply suggests that when one comes to high enough frequency, it too, could participate in the transportation process. \cite{schluter2009genetics}
To observe transportation of freshwater alleles in our simulations, we use a variety of metrics when sampling.
Throughout the simulation, we measure;
mutation frequencies, 
$F_{ST}$ values, \plr{how is $F_{ST}$ computed?}
average phenotype, 
mean number of original lakes each FAA appears in,
and total number of unique FAA. 
to understand where, as well as how much, of these freshwater haplotypes are being transported,
we track the mean percentage of FAA per individual (MPFAI) across all populations throughout the simulation:
computed as the sum of the FAA mutation frequencies among each population.
\plr{Define ``mean percentage''; no need to say that it is the sum of the frequencies, I think.}
\plr{Here FAA are defined in terms of the original populations, explaining why the introduced populations can have MPFAI of 0.
    This is counter-intuitive from the name (FAA); maybe we should call them ``pre-existing freshwater alleles''?
    ``standing genetic variants''?}
we're particularly interested in using MPFAI to measure the marine population' capacity to carry FAA,
as well as observing the introduced populations' ability to select upon them. 
\plr{omit this last sentence?}

@@

@@

We observed a dramatic shift in time until adaptation for the introduced populations
as migration rates increased. 
As can be seen in Figure \ref{fig:TimeToAdaptation} at the lowest migration rate of $5 * 10^{-5}$,
It took the introduced population over 30 thousand generations for the average phenotype of all the lakes to 
get to within 0.5 of the original lakes original phenotypes. 
\plr{From the plots it looks more like adaptation happens (at least in most lakes) by like 10K or 15K.}
This suggests that selection was acting primarily on new mutations, meaning the 
introduced lakes needed to wait for a beneficial mutation to arise before 
it was selected upon. 
\plr{We should do the calculation to see if this makes sense: 
    there's one new effect mutation in the right direction every 100 generations in the lakes,
    one of effect size $s$ has probability of about $s/2$ of not being lost to drift...}
There was a positive correlation between the amount of standing genetic variation in the 
marine and the rapid adaptation of the introduced populations.

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{matplotlibPlots/Power_FP.png}
  		\caption{ 
		Statistical Power and False Positives as a function of $F_{st}$ threshold. 
		Statistical Power is the likelihood that a SNP will be predicted to have an effect on phenotype when there is an effect to be detected (?).
		False Positives give us the ratio of SNPs that effect phenotype to total SNPs greater than the $F_{st}$ threshold.
		}
  		\label{fig:Power_FP}
	\end{center}
\end{figure}

@@

%\subsubsection*{Low Recombination Causes Clustering}
%\begin{comment}
\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-5.png}
  		\caption{ (PLACEHOLDER)
		}
  		\label{fig:Fst1}
	\end{center}
\end{figure}

@@

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-2.png}
  		\caption{(PLACEHOLDER)
		}
  		\label{fig:phenotype_ts4}
	\end{center}
\end{figure}
%\end{comment}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{comment}
\usepackage[backgroundcolor=pink,linecolor=red]{todonotes}
 \usepackage{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

@@

\newcommand{\plr}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}
\newcommand{\jgg}[1]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=black]{#1}}

@@

JARGON WE SHOULD THINK ON ??

Trait | Phenotype = Probably Trait

effect loci | QTL | causal: = ??

Original Lakes | $P_{1}$, $P_{3}$, $P_{3}$ = ?

Migration Rate | Introgression = ?

@@

% Jared's general notes for formatting

%\plr{``citep'' for ``cite in parentheses''. (and, citations come before the punctuation)}
%\plr{in latex, use ` `words' ' to get the open- and closed-double quotes (not the double-quote character)}
%\plr{"citet" for "cite, as part of the text"}

\jgg{Starting a paper is awkward, help}
The rate and tempo of evolution remains largely unknown.
Today, we have found multiple examples as evidence of rapid evolution 
in tens of generations or fewer.
Biologists are now starting to address the complexity behind ecological speciation. 
\jgg{Peter and Bill: Could use help with examples of rapid evolution and the story leading up to stickleback right here}

Recently, multiple instances of similar (parallel) underlying genetic basis of rapid local adaptation has brought about 
questions surrounding the origins of adaptive alleles.
A empirical model is the alaskan populations of freshwater and marine Ninespine Stickleback fish.
In 1964, The Great Alaskan Earthquake caused an uplift of Middleton island and in turn,
introduced a group of freshwater ponds around the perimeter of the island. 
Quickly inhabited by the surrounding marine population of Stickleback,
\citet{LescakE7204} observed significant phenotypic changes in less than 50 years that appear to be 
parallel to freshwater stickleback that have been separated for over $13,000$ years.
In freshwater stickleback, the number of lateral plates are reduced
and the opercle shapes shows the same expansion of the dorsal region and reduction of the ventral region.
\jgg{Bill - more specifics about Bill, Suzie, Kristin  \& or Thom's papers .. ? }
These results leave us with questions surrounding the nature of rapid adaptation.
Does convergent evolution breed it's own solution (haplotype) for every new selective pressure, 
or can these solutions can be efficiently shared across multiple sub - populations facing similar selective pressures.

The leading hypothesis for stickleback is that rather than acting on new mutations, 
adaptation to freshwater environments is sped up through selection on standing genetic variation (SGV) found in marine populations. 
\jgg{Bill: maybe you could make this section a little more specific}
One clear example of this is the gene \textit{eda} 
which has been shown to regulate the number of lateral plates. 
While this gene arose millions of years ago, it is found in freshwater ponds which have formed much more recently.
Novel evidence from natural populations has provided evidence that most regions of the genome that distinguish marine-freshwater genetic differences share this pattern. \cite{Nelson2017} 
\citet{schluter2009genetics} 
suggested the ``transporter''-hypothesis.  
This outlined the flow of freshwater alleles into marine populations through offspring of hybridization events.
It suggests freshwater haplotypes are distributed though marine individuals and are continually selected upon in introduced freshwater populations.
The continued selection on freshwater favored alleles and introgression between the two sub-species,
allows the marine to maintain the freshwater haplotype dispersed in low frequency among its' individuals. 
Once a new freshwater environment is introduced and inhabited by marine individuals who carry freshwater adapted alleles, selection reconstructs the freshwater haplotype. \cite{schluter2009genetics} 
An alternative to this hypothesis is that individuals from other freshwater environments migrate directly to the new environments, 
and their haplotype is passed down directly. 
This hypothesis has been shown to be unlikely due to finding a high frequency of freshwater alleles in the ocean,
and almost no freshwater individuals.

\plr{Bring up the possibility of more than one freshwater haplotype here.}
\jgg{Re: should I? Doesn't Thom's work and parallel above suggest they have the same alleles?}

If selection on SGV is key in rapid adaptation, 
many questions are brought to light concerning the surrounding population genetics parameters and underlying genomic architecture.
How rapidly can selection act on standing genetic variants at a given value of migration, $M$?
How many alleles underly a certain trait? (expand here)
Furthermore, how can we infer causal loci for regions of the genome that must be driving the rapid adaptation, from real data.
Many biologist today make use of genome wide association studies (GWAS) and 
$F_{st}$ across the genome to estimate regions responsible for certain traits. 
Unfortunately, the data can be heavily influenced by the level of introgression and population structure of the samples. 
This being the case, what are the biases we can expect to see in real data for certain levels of introgression.

There are many different parameters that carry a large impact on the questions above.
\citet{Ralph2015} 
explored the dichotomy of selection on new alleles and those brought in by migrants from a similar selective pressure.
This lead to an understanding of the process by which alleles move from an existing 'patch' to an introduced 'patch' with the 
same selective pressure. 
%read though Peter's paper more and connect it to what we're doing here.

In this paper, we explore time to local adaptation as a function of migration rate through an environment (marine) with opposing selective pressure. 
Next, we compare to real data and explore how $F_{st}$ data can be impacted by introgression, or lack of.
%Explain what we do and what we find that is important

%We use forward moving simulations to model marine and freshwater populations of stickleback.
%We then observe the effect (focusing on migration and recombination, for now) 
%of different parameters on local adaptation of introduced freshwater environments.

\section{Simulation Model}

Our simulations are forward-moving evolutionary models which
emulate the geography, selective pressure, and genomic architecture 
of coastal marine and freshwater lake populations. 
Here, we describe the specifics of out model.

\subsection*{life cycle}

For this study, we used a flexible evolutionary framework, SLiM \citep{Haller2017}.
The model-type we used was based off of an extended wright-fisher. 
The simulation life cycle of each generation is as follows.
First, generate offspring by:
(1) choosing parents based on cached fitness values and migration rates, 
(2) performing recombination of parental genomes, 
(3) allow for mutation, 
(4) modify each child by a defined callback. 
Next, offspring become individuals before fitness is evaluated for the next generation.
Finally, the generation counter is incremented. 
The population structure in SLiM can be arranged in any number of subpopulations, 
continuous or discrete, connected by any rate of migration.

\subsection*{Geography}

What we've modeled geographically is a coastal marine population 
connected by migration to multiple, smaller freshwater populations that are located along the coast.
The population structure for the marine is modeled as a one-dimensional, continuous population
ranging from 0.0 to 10.0.
There are two sets of lakes which represent freshwater populations; 
the first which evolves in parallel to the marine, 
and a set introduced later in the simulation as a subset of the marine. 
Each of the $10$ lakes, $i$, is located along the marine at $i - 0.5$, 
and connected by migration only through the marine environment. 
The marine has $2000$ individuals while 
each of the lakes fluctuate around $200$.

@@

\subsection*{Selective Pressure}

%(TALK ABOUT ADAPTEDNESS and TRADE-OFF), 
% abstracting real fish phenotype with `` trait value "

%Trait value is equal to the sum of the contribution of the effect loci and the loci may be 
%add, dom, recc. Uniformly chosen

To emulate the freshwater and marine selective pressure, 
we set up a quantitative genetics model in which fitness is phenotypically based. 
Freshwater and Marine environments are distinguished by a single numeric value. 
This number is the optimum trait value for each environment
and acts as a representation of lateral plate number and opercle shape in the stickleback populations.
%The fitness of an individual is then determined by a probability density for a normal distribution 
%at the quantile (?) of the difference between the optimum and the individual's phenotype
We use a Gaussian fitness function, 
where the fitness of an individual with trait $x$ in a population with optimal trait value $x_0$ is:
\begin{align}
    f(x; x_0) &= \exp\left(\frac{(x - x_0)^2 }{ 2 \sigma^2}\right),
\end{align}
with $\sigma = 15$.

Where a trait value, $x$, is also defined by a single numeric value; 
determined as a summation of the selection coefficients of all mutations an individual possesses. 
% no empty lines before equations, usually - they should read like part of the text itself.
%	\[
%{\textnormal{Individual.Phenotype = } \sum_{m \in mutations} \textnormal{m.selectionCoeff}}
%	\]

We allow six mutation types which affect phenotype along with one neutral mutation type.
Among the effect mutations; 
there are additive, dominant, and recessive mutations which a ffect phenotype
in either the positive or negative direction. 
The selection coefficients are pulled from a gamma distribution 
with a shape parameter of $1$ and a mean of either $0.5$, or ${-0.5}$. 
\plr{Can just say this in words, no need to have an equation.
    Also, a Gamma with shape 1 and mean 0.5 is an Exponential with mean 0.5.}

%	\[
%\textnormal{Mutation.selectionCoeff = } X \sim \Gamma (1,\pm0.5)
%	\]

@@

\subsection*{Genomic Architecture}

\plr{This should maybe come before the phenotype.}
In SLiM, the genome is conceptually a linear array of loci defining locations for 
mutations that arise and breakpoints for recombination. 
Genomic elements define a range depicting the types of mutations that can arise, and the ratio at which different mutation types can arise. 
Although still uncertain about how much of the genome is directly associated with the distinguished phenotypes, 
GWAS has indicated clusters of loci (linkage groups? Operon?) along the genome to be causative. 
To mimic this and compare dynamics of neutral vs. effect under selection, 
we create regions of effect. (???)
In these genomic elements of effect, we uniformly allow additive, recessive, and dominant, mutation that can push phenotype in either the positive or negative direction to arise. 
Every genomic position outside of these effect regions only allows for selectively neutral mutations to arise.

@@

@@

Here, we're interested in observing how different parameter values
(mainly migrations rates and recombination rates)
impact the sharing of alleles between populations. 
\plr{Below, I think we should make sure to use ``population'' to mean either ``lake'' or ``ocean'';
    so when we compute freshwater-marine $F_{ST}$ this measures differentiation between habitats,
    not between populations.}
we define freshwater adapted alleles (FAA),
\plr{I vote to remove the abbreviations. Also, should make the dependence on generation more clear: maybe ``freshwater adapted alleles at time $t$''?} 
at any given generation,
to be a mutations with a frequency higher than $0.5$ in \textit{any} of the original lakes, 
while remaining lower than $0.5$ in the marine. 
This is because the transportation hypothesis does not specify where or when an advantageous mutation arises; 
but simply suggests that when one comes to high enough frequency, it too, could participate in the transportation process. \cite{schluter2009genetics}
To observe transportation of freshwater alleles in our simulations, we use a variety of metrics when sampling.
Throughout the simulation, we measure;
%mutation frequencies, 
$F_{ST}$ values, \plr{how is $F_{ST}$ computed?}
average phenotype, 
mean number of original lakes each FAA appears in,
and total number of unique FAA. 
to understand where, as well as how much, of these freshwater haplotypes are being transported,
we track the mean percentage of FAA per individual (MPFAI) across all populations throughout the simulation:
computed as the sum of the FAA mutation frequencies among each population.
\plr{Define ``mean percentage''; no need to say that it is the sum of the frequencies, I think.}
%word this out better. 
\plr{Here FAA are defined in terms of the original populations, explaining why the introduced populations can have MPFAI of 0.
    This is counter-intuitive from the name (FAA); maybe we should call them ``pre-existing freshwater alleles''?
    ``standing genetic variants''?}
we're particularly interested in using MPFAI to measure the marine population' capacity to carry FAA,
as well as observing the introduced populations' ability to select upon them. 
\plr{omit this last sentence?}

@@

%Talk about the genetic basis of trait. 
%Talk about the progression of adaptation. How you can see introduction new alleles

@@

We observed a dramatic shift in time until adaptation for the introduced populations
as migration rates increased. 
As can be seen in Figure \ref{fig:TimeToAdaptation} at the lowest migration rate of $5 * 10^{-5}$,
It took the introduced population over 20 thousand generations for the average phenotype of all the lakes to 
get to within 0.5 of the original lakes original phenotypes. 
\plr{From the plots it looks more like adaptation happens (at least in most lakes) by like 10K or 15K.}
This suggests that selection was acting primarily on new mutations, meaning the 
introduced lakes needed to wait for a beneficial mutation to arise before 
it was selected upon. 
\plr{We should do the calculation to see if this makes sense: 
    there's one new effect mutation in the right direction every 100 generations in the lakes,
    one of effect size $s$ has probability of about $s/2$ of not being lost to drift...}
There was a positive correlation between the amount of standing genetic variation in the 
marine and the rapid adaptation of the introduced populations.

@@

\begin{figure}
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{matplotlibPlots/Power_FP.png}
  		\caption{ 
		%SP - suppose you have an Fst Peak, how likely is it that that region is causal. 
		Statistical Power and False Positives as a function of $F_{st}$ threshold. 
		Statistical Power is the likelihood that a SNP will be predicted to have an effect on phenotype when there is an effect to be detected (?).
		False Positives give us the ratio of SNPs that effect phenotype to total SNPs greater than the $F_{st}$ threshold.
		}
  		\label{fig:Power_FP}
	\end{center}
\end{figure}

%Suppose you have a Fst Peak, ___ how likely is it that that region is causal. and conversely, what proportion of 
%the causal loci are under Fst Peaks.

%

@@

%\subsubsection*{Low Recombination Causes Clustering}
\begin{comment}
\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/FstAcross5e-5.png}
  		\caption{ (PLACEHOLDER)
		}
  		\label{fig:Fst1}
	\end{center}
\end{figure}

@@

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.7\linewidth]{plotlyPlots/PhenotypeThroughout5e-2.png}
  		\caption{(PLACEHOLDER)
		}
  		\label{fig:phenotype_ts4}
	\end{center}
\end{figure}
\end{comment}
